maze-dataset: Algorithmic Variety and Representation Flexibility in Maze Generation

### 2025-04-08 docs/paper/paper.tex
provisional title

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Tilman Räuker, Brandon Knutson, Cecilia Diniz Behn, Samy Wu
Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Tilman Räuker, Brandon Knutson, Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Ivanitskiy
et al. (1970). maze-dataset. \emph{Journal of Open Source Software},
\emph{¿VOL?}(¿ISSUE?), ¿PAGE? \url{https://doi.org/N/A}}.}}

@@

\title{maze-dataset}

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset: Algorithmic Variety and Representation
Flexibility in Maze Generation},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Tilman Räuker, Brandon Knutson, Cecilia Diniz Behn, Samy Wu
Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Tilman Räuker, Brandon Knutson, Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Ivanitskiy
et al. (1970). maze-dataset: Algorithmic Variety and Representation
Flexibility in Maze Generation. \emph{Journal of Open Source Software},
\emph{¿VOL?}(¿ISSUE?), ¿PAGE? \url{https://doi.org/N/A}}.}}

@@

\title{maze-dataset: Algorithmic Variety and Representation Flexibility
in Maze Generation}
